Global case

### 2025-05-06 lipschitz/Lipitschz.tex
update

	MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in $\{0,1\}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding. As solving LP instances is polynomial time, this optimization is significantly more efficient. However, this efficiency comes at the cost of precision, often resulting in less stringent bounds. This approach is termed the {\em LP abstraction}. We invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof:

@@

	\subsubsection{Cloned model}

	The most straight way is to build two identical MILP models $M_1,M_2$ with completely disjoint variables (including inputs and outputs) with some extra constraints:

	\subsubsection{Simplified models}

>>>>

	MILP instances can be linearly relaxed into LP over-abstraction, where variables originally restricted to integers in $\{0,1\}$ (binary) are relaxed to real numbers in the interval $[0,1]$, while maintaining the same encoding. As solving LP instances is polynomial time, this optimization is significantly more efficient. However, this efficiency comes at the cost of precision, often resulting in less stringent bounds. This approach is termed the {\em LP abstraction}. We invoke a folklore result on the LP relaxation of (\ref{eq11}), for which we provide a direct and explicit proof.

@@

	\subsection{Cloned model}

	The most straight way is to build two identical MILP models $M_1,M_2$ with completely disjoint variables (including inputs and outputs) with some extra variables and constraints:

	\subsection{Simplified models}
